%Background body
%Created MB 03-01
%\usepackage{graphicx}
%\usepackage{setspace}
%\usepackage{color}
%\usepackage{amssymb}
%\usepackage{listings}
%\usepackage{epstopdf}

\section{Background}

Muons ($\mu^-$) and antimuons($\mu^+$) are the most numerous charged
particles at sea level\cite{pdg}. Most of them are produced at a
height of about $15$ km in decays of charged kaons and pions which are
formed via the interaction of cosmic ray particles with the Earth's
upper atmosphere \cite{amsler}. The muon is produced in a weak decays
as shown for example in Figure and at sea level forms $80\%$ of cosmic
ray flux.

\subsection{Muon Decay}

In free space, negatively charged muons decay weakly into an electron,
muon neutrino, and electron antineutrino \cite{easwar} (Figure):

\begin{equation}\mu^- \rightarrow e^- \nu_{\mu}\overline{\nu_e}\label{mudecay}\end{equation}

with a corresponding antimatter process of

\begin{equation}\mu^+ \rightarrow e^+ \overline{\nu_{\mu}}{\nu_e}\label{antimudecay}\end{equation}

The muon lifetime is approximately $2.2 \mu$s\cite{easwar}, second
only to the lifetime of the neutron. In matter, another decay is
possible for $\mu^-$ via nucleus capture:

\begin{equation}\mu^-p^+ \rightarrow n \nu_{\mu} \label{pcap} \end{equation}

(**insert stuff about the muon capture lifetime here**)

The decay of the muon is desribed by an exponential function

\begin{equation} N(t) = N_0 e^{-\Gamma_{\mu} t} \label{expdecay}\end{equation} 
here $\Gamma_{\mu}$ is the decay rate, which gives the decay lifetime
$\tau_{\mu} = 1/\Gamma_{\mu}$.

In this experiment, we measure the time between the start event, when
a $\mu^- (\mu^+)$ comes to rest in a scintillator in the lab and the
stop event, which signals the emission of $e^- (e^+)$ in the muon
decay. The histogram of the recorded times is then fit to \eqref{expdecay} to
give the lifetime of the muon.

\subsection{Effects of Relativistic Time Dilation}

Even with velocities within a percent of the speed of light, the
travel time of the muon from the point of creation in the atmosphere
takes approximately $50\mu$s - over 20 decay lifetimes - to reach the
ground. According to Newtonian physics, the flux would be reduced by a
factor of over $10^{10}$. However, the flux of muons at sea level,
where the lab is located, remains large at $10^{-2}$
cm$^-2$s$^-1$sr$^-1$, only reduced by a factor of $5$ from the peak
flux at $15$km \cite{rossi}.

This effect is due to the relativistic time dilation predicted by
Special Relativity. While in the frame of the laboratory, the time of
flight of the muons is $50\mu$s, the muon itself experiences a proper
time reduced by a factor of $\gamma$: $t_{\mu} = \gamma t_{lab}$,
where $\gamma = 1/\sqrt{1 - \frac{v^2}{c^2}}$. Since the particles are
travelling close to the speed of light, the relativistic correction
becomes non-negligible. With muon speeds ranging from $.994c$ to
$.998c$, the proper time experienced by the muon is between $3.2$ and
$5.5\mu$s, less than $2$ lifetimes on average. 

The time in flight is still on the same order, and even greater than,
the lifetime of muon decay which our experiment seeks to
measure. Nevertheless, the time the muons experience in the atmosphere
prior to stopping in the detector has no effect on the decay rate
measurement. While we do sample fewer short decay times and slow
moving muons, this fact simply decreases the amount of data without
affecting the parameters of the exponential.

\subsection{Muon Mass}



\subsection{Weak Force Coupling Constant}

The decay rate $\Gamma_{\mu}$ is proportional to the square of the
amplitude of the decay diagram (Figure ~\ref), which depends on the
product of the couplings at each vertex. In this case, the coupling at
each of the two vertices is proportional to $\sqrt{G_F}$, the Fermi
constant, so we have

\begin{equation}\Gamma_{\mu} \propto G_F^2 \end{equation}

A more involved calculation gives that the lifetime of the muon is 

\begin{equation}\tau_{\mu} = \dfrac{192\pi^3\hbar^7}{G_F^2m_{\mu}^5c^4}\end{equation}
where $c$ is the speed of light, $\hbar$ is Planck's constant, and
$m_{\mu}$ is the rest mass of the muon. 

Once we establish the value of $m_{\mu}$, we can find the Fermi
constant $G_F$ and the 

The weak decay of the muon is the clearest of all weak interaction
phenomena in both its experimental and theoretical aspects. Thus, the
muon decay is an effective means of studying the weak force, and
specifically finding the weak coupling constant $g_w$.


\begin{equation}\end{equation}
